---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fairenough

<!-- badges: start -->

[![R-CMD-check](https://github.com/openwashdata/fairenough/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/openwashdata/fairenough/actions/workflows/R-CMD-check.yaml)
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)

<!-- badges: end -->

The goal of `fairenough` is to provide tools to make the [openwashdata data package](https://openwashdata.org/pages/gallery/data/) workflow consistent and efficient.

## Installation

The easiest way to get started with `fairenough` is by installing it from CRAN:

```{r, eval=FALSE}
install.packages("fairenough")
```


To get the latest version, you can install the development version from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("openwashdata/fairenough")
```

## How to use fairenough

To learn more about `fairenough`, check out the 'Get Started' page. This, along with the 'Reference' page, will give you a good overview of the toolkit.

If you decide to use `fairenough` for publishing your data (which we hope you will!), take a look at our [detailed guide](https://global-health-engineering.github.io/ghedatapublishing/). It's regularly updated and walks you through the entire process.
