---
title: "Get started with fairenough"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with fairenough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

The `fairenough` package offers an easy-to-use toolkit to publish your WASH data. This guide provides simple steps to get the package up and running on your machine.

To install the latest stable version of `fairenough` from CRAN, use the following command in your R console:

```{r}
install.packages("fairenough")
```

If you’d like to try out the latest features and improvements, you can install the development version of `fairenough` from GitHub. Make sure you have the `remotes` package installed:

```{r}
# Install fairenough from GitHub
remotes::install_github("openwashdata/fairenough")
```

After installing `fairenough`, you can start using its functions in your WASH data publication workflow! For a detailed guide on how to get set up and an overview of the package features, visit the full guide [here](https://global-health-engineering.github.io/ghedatapublishing/).


Happy coding with `fairenough`!
