---
title: "fairenough demo: turning palmerpenguins into a data package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fairenough demo: turning palmerpenguins into a data package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# This vignette uses palmerpenguins as input data. If it's not
# installed, the whole vignette is skipped so we never block
# package builds in environments without it.
penguins_available <- requireNamespace("palmerpenguins", quietly = TRUE)
knitr::opts_chunk$set(eval = penguins_available)
```

```{r needs-palmerpenguins, eval = !penguins_available, echo = FALSE, results = "asis"}
cat("> This vignette requires the **palmerpenguins** package. Install it with `install.packages(\"palmerpenguins\")` and rebuild the vignette to see the demo.\n")
```

`fairenough` turns a tidy data file into a fully-documented R data package. This vignette walks through the full pipeline on the well-known Palmer penguins dataset, ending with the resulting package layout.

We do every step in a throw-away project so nothing leaks into your real working directory.

```{r workspace}
library(fairenough)

# Disposable working directory; cleaned up automatically.
project <- withr::local_tempdir()

# Drop a CSV of penguins into the project root — exactly what a user
# would have when they start.
write.csv(
  palmerpenguins::penguins,
  file.path(project, "penguins.csv"),
  row.names = FALSE
)
```

## Step 1: `setup()`

`setup()` scaffolds the standard data-package layout (`R/`, `data/`, `data_raw/`, `inst/extdata/`), moves the input CSV into `data_raw/`, and configures `.gitignore`.

```{r step-setup}
setup(
  base_path = project,
  verbose = FALSE,
  overwrite = TRUE
)
```

## Step 2: `process()`

`process()` reads everything in `data_raw/`, applies `janitor::clean_names()` to the column headers, and writes both a binary `.rda` (for `data()` access) and a tidy `.csv` (for download) per dataset.

```{r step-process}
process(base_path = project, verbose = FALSE)
```

## Step 3: `collect()`

`collect()` gathers the metadata that lives in `DESCRIPTION` — title, description, authors, license, etc. Normally it walks the user through interactive prompts, but every field can also be supplied as a named argument, which is what we do here.

```{r step-collect}
collect(
  base_path = project,
  interactive = FALSE,
  verbose = FALSE,
  overwrite = TRUE,
  pkg_name = "penguinpkg",
  title = "Palmer Penguins as an R Data Package",
  description = "Body size measurements for three penguin species observed on islands in the Palmer Archipelago.",
  license = "mit",
  authors = list(
    list(
      given = "Demo",
      family = "Author",
      email = "demo@example.org",
      roles = c("aut", "cre")
    )
  )
)
```

## Step 4: `generate()`

`generate()` produces a per-variable dictionary at `inst/extdata/dictionary.csv`. Pass an `ellmer::chat()` object to fill the `description` column from an LLM; pass `NULL` (or no `chat`) to get the same dictionary with empty descriptions, which you can edit by hand.

For a working vignette without an API key, we use a small stand-in object that duck-types the `chat` interface — the same trick the package's tests use.

```{r step-generate}
# Stand-in for an ellmer chat object. In real usage you'd write:
#   chat <- ellmer::chat_openai(model = "gpt-4o-mini")
fake_chat <- local({
  i <- 0
  list(chat = function(prompt) {
    i <<- i + 1
    sprintf("Demo description for variable #%d", i)
  })
})

generate(
  base_path = project,
  chat = fake_chat,
  verbose = FALSE,
  overwrite = TRUE
)
```

## Step 5: `build()` (not run here)

`build()` is the final, heaviest step: it generates roxygen docs from the dictionary, writes `inst/CITATION` and `CITATION.cff`, runs `R CMD build` + `R CMD INSTALL`, knits the README, and builds the pkgdown site. We skip the call inside this vignette to keep the build fast, but the one-liner is just:

```{r step-build, eval = FALSE}
build(base_path = project, verbose = FALSE, preview = FALSE)
```

## The result

Here is everything `fairenough` produced under `project/`:

```{r tree}
fs::dir_tree(project, recurse = TRUE)
```

That's a complete, installable R data package created from a single CSV — ready for `R CMD build`, GitHub, or CRAN.
