---
output: github_document
always_allow_html: true
editor_options:
  markdown:
    wrap: 72
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)

library(desc)
library(dplyr)
library(readr)
library(gt)
library(kableExtra)
library(fontawesome)
library(stringr)

# --- Define a list of package names ---
package_names <- list.files("inst/extdata", pattern = "\\.csv$", full.names = FALSE)
package_names <- basename(package_names) # Get just the base names
package_names <- package_names[!package_names %in% "dictionary.csv"]
package_names <- stringr::str_remove(package_names, "\\.csv$") # Remove .csv extension


organisation <- desc::desc_get_field("Organisation") # Assuming you have an 'Organisation' field in DESCRIPTION
browser_favicon_colour <- "lightblue"
```

# `r desc::desc_get_field("Package")`

***`r desc::desc_get_field("Title")`***

<!-- badges: start -->

[![License: CC BY
4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.15554776.svg)](https://zenodo.org/doi/10.5281/zenodo.15554776)

<!-- badges: end -->

-----

## Installation

You can install the development version of `r desc::desc_get_field("Package")` from GitHub `r fontawesome::fa("github")` with:

```r
devtools::install_github("`r organisation`/`r desc::desc_get_field("Package")`", dependencies = TRUE)
```

-----

### Download as CSV Files

If you prefer to work with the data outside of R, you can download individual datasets as CSV files.

1.  **Right-click** on the "Download CSV" link for the dataset you want.
2.  Select **"Save Link As"** [`r fontawesome::fa("chrome", fill = browser_favicon_colour)`](https://www.google.com/chrome/) [`r fontawesome::fa("edge", fill = browser_favicon_colour)`](https://www.microsoft.com/edge/) [`r fontawesome::fa("firefox", fill = browser_favicon_colour)`](https://www.mozilla.org/firefox/) or **"Download Linked File"** [`r fontawesome::fa("safari", fill = browser_favicon_colour)`](https://www.apple.com/safari/).
3.  Choose where you'd like to save the file on your computer.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
extdata_path <- paste0(desc::desc_get_field("URL"), "/raw/main/inst/extdata/")

readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::distinct(file_name) |>
  dplyr::mutate(file_name = stringr::str_remove(file_name, "\\.rda$")) |> # Ensure .rda is removed
  dplyr::rename(dataset = file_name) |>
  dplyr::mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)")
  ) |>
  knitr::kable()

```

## Data

```r
library(`r desc::desc_get_field("Package")`)
```

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# Iterate through each package name and generate content
for (pkg_name in package_names) {
  cat("\n---\n\n") # Separator for each dataset

  # Conditionally load data if it's not already in the environment
  # Assuming 'pkg_name' is also the name of the dataset object once loaded
  if (!exists(pkg_name)) {
    data(list = pkg_name, package = desc::desc_get_field("Package"))
  }

  current_data <- get(pkg_name)

  cat(paste0("### ", pkg_name, "\n\n"))
  cat(paste0("The dataset `", pkg_name, "` has `", nrow(current_data), "` observations and `", ncol(current_data), "` variables\n\n"))

  # Display head of the dataframe using gt
  cat("```r\n")
  cat(paste0("get(\"", pkg_name, "\") |> \n"))
  cat("  head(3) |> \n")
  cat("  gt::gt() |> \n")
  cat("  gt::as_raw_html()\n")
  cat("```\n\n")

  # Render the gt table in the Rmd output
  print(
    current_data |>
      head(3) |>
      dplyr::mutate(
        across(where(is.character), ~ stringr::str_trunc(., width = 50, ellipsis = "..."))
      ) |> 
      gt::gt() |>
      gt::as_raw_html()
  )

  cat("\n\n") # Newlines for spacing

  # Overview of variable names
  cat("For an overview of the variable names, see the following table.\n\n")
  
  # Filter dictionary for the current dataset
  dictionary_table <- readr::read_csv("data-raw/dictionary.csv") |>
    dplyr::filter(file_name == paste0(pkg_name, ".rda")) |> # Ensure matching .rda
    dplyr::select(variable_name:description)

  if (nrow(dictionary_table) > 0) {
    print(
      dictionary_table |>
        knitr::kable(booktabs = TRUE) |>
        kableExtra::kable_styling(
          full_width = FALSE,
          bootstrap_options = c("striped"),
          position = "center"
        )
    )
  } else {
    cat("No dictionary entry found for this dataset.\n\n")
  }
}
```

## License

Data are available as
[CC-BY](https://github.com/`r desc::desc_get_field("Organisation")`/`r desc::desc_get_field("Package")`/blob/main/LICENSE.md).

## Citation

```{r, echo=FALSE, message=FALSE, warning=FALSE}
citation(desc::desc_get_field("Package"))
```
